Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-26 prop_letter.tex
prop_letter.tex \paragraph{Quantum Interval-valued Probability Measures ({\rm IVPMs})} Update a little bit...

To formalize the idea of finite precision measurement, we next introduce 
the notion of quantum IVPM~$\bar{\mu}$. The latter replaces 
the infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$ of
intervals. Since the intervals $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$ 
should be included in $\mathscr{I}$, and arithmetic operations on intervals satisfy
\begin{subequations}\label{eq:interval-operations}
\begin{eqnarray}
 &  & \left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right], \textrm{ and}\\
 &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}] ,
\end{eqnarray}
\end{subequations}
$\bar{\mu}:\events\rightarrow\mathscr{I}$ is defined by the axioms:
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item 
$
\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
$
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
$P_iP_j=\delta_{ij}P_i$, 
we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
Notice that Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
to inclusion because the equality is usually too strong to hold. For
example, if we consider $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $
and $\bar{\mu}\left(P\right)=\left[l,r\right]$, by Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement})
and (\ref{eq:interval-operations}), we have 
\[
\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1+l-r,1+r-l\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)
\]
when $r>l$.

>>>>

To formalize the idea of finite precision measurement, we next introduce 
the notion of quantum IVPM~$\bar{\mu}$. The latter replaces 
the infinitely precise interval $[0,1]$ by a finite collection $\mathscr{I}$ of
intervals. Since the intervals $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$ 
should be included in $\mathscr{I}$, and arithmetic operations on intervals satisfy
\begin{subequations}\label{eq:interval-operations}
\begin{eqnarray}
 &  & \left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right], \textrm{ and}\\
 &  & [l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}] ,
\end{eqnarray}
\end{subequations}
$\bar{\mu}:\events\rightarrow\mathscr{I}$ is defined by the axioms:
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
$P_{i}P_{j}=\delta_{ij}P_{i}$, we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
Notice that Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
to inclusion because the equality is usually too strong to hold. For
example, if we consider $\left\{ P_{1},P_{2}\right\} =\left\{ P,\mathbb{1}-P\right\} $
and $\bar{\mu}\left(P\right)=\left[l,r\right]$, by Eq.~(\ref{eq:interval-operations}),
we have 
\[
\bar{\mu}(\mathbb{1})=\left[1,1\right]\subsetneq\left[1+l-r,1+r-l\right]=\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)
\]
when $r>l$.
